Robust background subtraction in traffic environments

### 2019-02-07 paper/Paper.tex
Intro

\subsection*{Introduction}

>>>>

\subsection*{Introduction}
Background subtraction and foreground detection are the basic tasks of many real application systems,
for example, surveillance systems, autonomous vehicles, semantic image analysis. Background subtraction
consists in finding a category for every pixel in a single or (like in this case) in a frames sequence
of a video and saying if that pixels are part of background or foreground. At the end, the algorithm take as
as input a video and output a binary mask, where 1s are foreground pixels and 0 background pixels.
We restricted our domain to traffic monitoring, in particular this work should put the basis for an automated
tool to identify cars and detect anomalies in highways and roads 24/24h (e.g. car accidents,
traffic jam, wrong-direction driving) using a standard RGB stationary camera.
Critical aspects that must be taken into account while
developing such algorithm are a lot, first of all, variable and bad weather conditions and illumination
changes. In fact, it is very hard to distinguish moving objects in presence of heavy rain, fog or snow.
Also during night the environmental situation varies a lot from the day and our algorithm has to adapt
continuosly due to this facts. Other problems that we faced are shadows and intermittent object motion.
From the majority of the current algorithms, shadows are treated as foreground because they move along with
objects; a little number of them adopts a 3-class classification (background, foreground, shadow). We
decided to provide a binary classification, considering shadows as part of the background. With regards to
the latter problem, here the challenge is to correctly detect an initially stationary object that begins to
move or when an object that was static starts moving again. We fine-tuned some parameters to make sure
that a moving car that stops after a while will be classified as foreground for a long time before turning
into background, while the opposite event (from static to moving) is easier to handle.
The entire algorithm has been implemented in C++, since compiled code performances are fundamental to
allow the system to work in real-time. In \cite{pbasandsceneanalysisfpga}, we can find an integration of the basic algorithm in
a FPGA device, which exploit and hardware implementation to reduce a lot the computational time.
